---
title: "Light_Spactrum"
author: "Laksara_Abeysinghe"
date: "July 27, 2021"
output:
  html_document: default
  word_document: default
---
The researcher has used light spactrum (as treatment with 3 different levels: Red, Blue, Control) for measure germination potential how they are significantly differing.  
* He has measured different responses factors. Such as,

  + Germinated_seeds(%),
  + Total_seedling_Length, 
  + Total_Length, 
  + Leaf_Length,
  + Leaf_Width.

```{r data_file, message=FALSE, warning=FALSE, paged.print=FALSE}
(df <- read.table("Light_Spectrum.csv", header = TRUE, sep = ","))
```

#ANOVA Models
  
```{r Analyze models, message=FALSE, warning=FALSE, paged.print=FALSE}
library(dplyr)
Lights <- as.factor(df$Light_Spectrum)
x <- list(
  df$Germinated_seeds...,
  df$Total_seedling_Length, 
  df$Total_Length, 
  df$Leaf_Length,
  df$Leaf_Width
  )

models <- function(x) {
  ANOV <- vector("list", length(x))
  for (i in seq_along(x)) {
    ANOV[[i]] <- anova(lm(x[[i]] ~ Lights))
  }
  ANOV
} 

results <- models(x)
names(results) <- c( "Germinated_seeds...", "Total_seedling_Length", 
                      "Total_Length", "Leaf_Length", "Leaf_Width")
results

```

So according to these results we can conclude that outputs by hypothetically as,

Null hypothesis (H0)   :- There is same effect of 3 type of light spacrtrum on four different factors.

Alternative hypothesis (H1)   :-The effects on four different factors are not all the same. (At least on pair of light spactrum are different).


```{r p_value_table, message=FALSE, warning=FALSE, paged.print=FALSE}
p_val <- vector("double", length(results))
concl <- vector("double", length(results))
for (i in seq_along(results)) {
  p_val[[i]] <- results[[i]][[5]][1]
  concl[[i]] <- ifelse(p_val[[i]] < 0.05, "Significant", "Not_Significant")
}

P_Results <- tribble(
  ~Factor,
  "Germinated_seeds...", "Total_seedling_Length", 
  "Total_Length", "Leaf_Length", "Leaf_Width"
) %>%
  mutate(P_Values = p_val, Conclusions = concl)

(P_Results)

```

In above graph we can see 3 type of lights spactrum have significantly different on all different factors.
*(All p_values are less than the alpha (0.05) value)*


#Mean Comparisons

```{r mean_comparisions, message=FALSE, warning=FALSE, paged.print=FALSE}
comparisions <- function(x) {
  comp <- vector("list", length(x))
  for (i in seq_along(x)) {
    comp[[i]] <- TukeyHSD(aov(lm(x[[i]] ~ Lights)))
  }
  comp
} 
mean_com <- comparisions(x)
names(mean_com) <- c( "Germinated_seeds...", "Total_seedling_Length", 
                      "Total_Length", "Leaf_Length", "Leaf_Width")
mean_com
```


In here we can conclude what group exactly differ from the control group. That is in hypothetically *(Reject H0 when p_value is less than the alpha(0.05) value)*

H0 :- mean(i) = mean(control)

H1 :- mean(i) != mean(control )  for some i,    (mean(i): mean of each treatment)
  
  
According to these results we can see basically, 

+Two types of factor levels are significantly different from the control group *("Total_seedling_Length", "Total_Length")* and 

+Two types of factor levels are not significantly different from the control group *("Germinated_seeds(%)", "Leaf_Width")*.

+In *("Leaf_Length")* factor Blue light spectrum is signifficantly different from the control group and Red light spectrum is not.

Factor                 | Light spectrum  | From Control Group
---------------------- | --------------- |----------------------------
Germinated_seeds(%)    | Red             | Sgnificantly Not Different
  -                    | Blue            | Sgnificantly Not Different
Total_seedling_Length  | Red             | Sgnificantly Different
  -                    | Blue            | Sgnificantly Different
Total_Length           | Red             | Sgnificantly Different
  -                    | Blue            | Sgnificantly Different
Leaf_Lengt             | Red             | Sgnificantly Not Different
  -                    | Blue            | Sgnificantly Different
Leaf_Width             | Red             | Sgnificantly Not Different
  -                    | Blue            | Sgnificantly Not Different


